Automated detection of data fabrication using statistical tools

### 2018-03-27 submission/redraft.rmd
Add two paragraphs

@@

>>>>

```{r table_excess, echo = FALSE}
knitr::kable(df, digits = 3, caption = "Examples of means and standard deviations for a continuous outcome in genuine- and fabricated randomized clinical trials. Set 1 (S1) is randomly generated data under the null hypothesis of random assignment (assumed to be the genuine process), whereas Set 2 (S2) is generated under excessive consistency with equal groups. Each trial condition contains 100 participants. The $p$-values are the result of independent $t$-tests comparing the experimental and control conditions within each respective set.")
```

@@

```{r, echo = FALSE}
threshold <- .05
genuine_p <- ex1_1tp[ex1_1tp > threshold]
fab_p <- ex2_1tp[ex2_1tp > threshold]
genuine_chi <- -2 * sum(log(1 - ((genuine_p - threshold) / (1 - threshold))))
fab_chi <- -2 * sum(log(1 - ((fab_p - threshold) / (1 - threshold))))
genuine_chi_p <- pchisq(q = genuine_chi, df = 2 * length(genuine_p), lower.tail = FALSE)
fab_chi_p <- pchisq(q = fab_chi, df = 2 * length(fab_p), lower.tail = FALSE)
x <- c(.21, -.08, -.37, -.08, .32)
pval <- pnorm(abs(x), 0, 1, lower.tail = FALSE) * 2
pval <- pval[pval > threshold]
chi <- -2 * sum(log(1 - ((pval - threshold) / (1 - threshold))))
p_chi <- pchisq(q = chi, df = 2 * length(pval), lower.tail = FALSE)
```

As an example, we apply the reversed Fisher method to both the genuine- and fabricated results. 
Using the threshold $t=`r threshold`$ to only select the nonsignificant results from Table xxxx, we retain $k=`r length(genuine_p)`$ genuine $p$-values and $k=`r length(fab_p)`$ fabricated $p$-values. 
This results in $\chi^2_{2\times`r length(genuine_p)`}=`r round(genuine_chi, 3)`,p=`r round(genuine_chi_p, 3)`$ for the genuine data from Table xxxx; $\chi^2_{2\times`r length(fab_p)`}=`r round(fab_chi, 3)`,p=`r round(fab_chi_p, 3)`$ for the fabricated data from Table xxxx. 
Another more practical example directly from the Fuji case [@10.1111/j.1365-2044.2012.07128.x], anecdotally illustrates that actual fabricated data can result in significant findings with the reversed Fisher method. 
For example, $p$-values extracted from the original Table 3 [fentanyl dose; @10.1111/j.1365-2044.2012.07128.x] for five independent comparisons show excessively high $p$-values, $\chi^2_{2\times`r length(pval)`}=`r round(chi, 3)`, p=`r round(p_chi, 3)`$.

We note that misspecified one-tailed tests can also result in excessive amounts of large $p$-values.
For correctly specified one-tailed tests, the $p$-value distribution is right-skewed if the alternative hypothesis is true. 
When the alternative hypothesis is true, but the effect is in the opposite direction of the hypothesized effect (e.g., a negative effect when a one-tailed test for a positive effect is conducted), this results in a left-skewed $p$-value distribution.
As such, any data fabrication detected with this method would need to be inspected for misspecified one-tailed hypotheses to preclude false conclusions. 
In the studies we present in this manuscript, misspecification of one-tailed hypothesis testing is not an issue because we prespecified the effect and its direction to the participants.
